My title

### 2024-12-02 paper/paper.qmd
updated libraries
updated introduction

library(tidyverse)
library(palmerpenguins)
library(arrow)
library(here)

@@

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

>>>>

library(tidyverse)
library(palmerpenguins)
library(arrow)
library(here)
library(readr)
library(usethis)
library(dplyr)
library(testthat)
library(rstanarm)
library(ggplot2)
library(brms)

@@

////Overview paragraph////
The Ministry of Home Security was the British government department established in 1939 to direct the response to German air raids. Part of its responsibility was tracking data related to air raids. This data

////Estimand paragraph////
The estimand is the number of casualties sustained during an attack. I use the Home Security data with a multiple linear regression model to estimate the difference in casualties during nighttime air raids compared to daytime air raids

////Results paragraph////

////Why it matters paragraph////
